---
title: 'A Hierarchical Bayesian Approach to Small Area Estimation of Forest Attributes'
author: 'Grayson White'
date: 'May 2021'
institution: 'Reed College'
division: 'Mathematics and Natural Sciences'
advisor: 'Kelly McConville' 
department: 'Mathematics'
degree: 'Bachelor of Arts'
knit: bookdown::render_book
site: bookdown::bookdown_site
params:
  'Install needed packages for {thesisdown}': True
output:
  thesisdown::thesis_pdf: default 
#  thesisdown::thesis_gitbook: default         
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default

# If you are creating a PDF you'll need to write your preliminary content 
# (e.g., abstract, acknowledgements) below or use code similar to line 25-26 
# for the .RMD files. If you are NOT producing a PDF, delete or silence
# lines 25-39 in this YAML header.
abstract: '`r if(knitr:::is_latex_output()) paste(readLines(here::here("prelims", "00-abstract.Rmd")), collapse = "\n  ")`'
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab 
# is needed on the line after the `|`.
acknowledgements: |
  This is where acknowledgements will go. 
dedication: |
  To my family. 
preface: |
  This is an example of a thesis setup to use the reed thesis document class 
  (for LaTeX) and the R bookdown package, in general.
  
# Specify the location of the bibliography below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
---

```{r include_packages, include=FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if (!require(remotes)) {
  if (params$`Install needed packages for {thesisdown}`) {
    install.packages("remotes", repos = "https://cran.rstudio.com")
  } else {
    stop(
      paste('You need to run install.packages("remotes")",
            "first in the Console.')
    )
  }
}
if (!require(thesisdown)) {
  if (params$`Install needed packages for {thesisdown}`) {
    remotes::install_github("ismayc/thesisdown")
  } else {
    stop(
      paste(
        "You need to run",
        'remotes::install_github("ismayc/thesisdown")',
        "first in the Console."
      )
    )
  }
}
library(thesisdown)
# Set how wide the R output will go
options(width = 70)
```


```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00--prelim.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("prelims", "00-abstract.Rmd")}

```

# Introduction {.unnumbered}

In order to implement and fully explore the behavior of these hierarchical Bayesian estimators, we must introduce concepts, theory, and specifics related to the research question at hand. An overview of how we approach the research throughout this thesis is below:

* Chapter \@ref(data) introduces the data used to accomplish our research goal. We discuss the nested structure of the data and how it lends itself to hierarchical modeling. We explore the spatial aspects of our response variables and the distributions of these variables. We also introduce the data used for our explanatory variable and the data used for strata weighting.
* Chapter \@ref(methods) builds up the theory and mathematics behind the estimators used in this thesis. Starting at the simplest case of the sample mean, we progressively introduce new estimators which take varying levels of information into account. We also introduce some theory regarding Bayesian statistics in order to build intuition for our hierarchical Bayesian estimators.
* Chapter \@ref(results) showcases the results of each estimator's performance. We discuss strengths and weaknesses of estimators implemented. These results are explored spatially and we gain insight into regions where particular estimators reduce variance more than others.
* Chapter \@ref(discussion) discusses the key findings of this thesis, the limitations regarding these findings, and possible extensions of the work done in this thesis.